Analysis and figures

### 2021-04-17 analysis/03_analysis.Rmd
Look at religions for reviewer

  tar_load(sim_excel_final)
  tar_load(sim_final)
  tar_load(giving_aggregate)
  tar_load(giving_per_capita)
})
```

>>>>

  tar_load(survey_results)
  tar_load(sim_excel_final)
  tar_load(sim_final)
  tar_load(giving_aggregate)
  tar_load(giving_per_capita)
})
```

# General demographics of recipients

## Religion

```{r plot-religion}
religion_lookup <- tribble(
  ~Q5.10, ~religion,
  1, "Catholic",
  2, "Protestant",
  3, "Christian Orthodox",
  4, "Jewish",
  5, "Muslim",
  6, "Sikh",
  7, "Hindu",
  8, "Buddhist",
  9, "Atheist",
  10, "Other"
)

n_respondents <- nrow(survey_results)

religions <- survey_results %>% 
  count(Q5.10) %>% 
  left_join(religion_lookup, by = "Q5.10") %>% 
  arrange(n) %>% 
  mutate(religion = fct_inorder(religion)) %>% 
  mutate(percent = n / n_respondents)

ggplot(religions, aes(x = n, y = religion)) +
  geom_col(fill = clrs_okabe_ito$reddish_purple) +
  scale_x_continuous(sec.axis = sec_axis(~. / n_respondents, labels = percent)) +
  labs(x = "Number of respondents", y = NULL) +
  theme_ngo()
```

```{r religion-others}
religion_others <- survey_results %>% 
  filter(!is.na(Q5.10_TEXT)) %>% 
  mutate(Q5.10_TEXT = str_to_lower(Q5.10_TEXT)) %>% 
  count(Q5.10_TEXT) %>% 
  arrange(desc(n))
religion_others
```
